A note on multi agent learning

### 2016-06-28 multiAgentLearning/paper/article.tex
added the tables and descriptions

\section{Iterated prisoner's dilemma}
\todo{make an intermezzo of this?}
\drafting
To demonstrate a potential use of this algorithm we will use at several example
cases. The first one being the iterated prisoner's dilemma. Consider
the following normal form game:

@@

\begin{tabular}{lllll}
    t & Cooperate & $A_t$ & $\pi_t$ & $\alpha_t$ \\
    0 & C     & C    & 3       & 4 \\
    1 & C     & D    & 4       & 3.5 \\
    2 & C     & D    & 4       & 3.75 \\
\end{tabular}

@@

\begin{tabular}{lllll}
  t & Coop & $A_t$ & $\pi_t$ & $\alpha_t$ \\
  0 & C     & C    & 3       & 2 \\
  1 & C     & C    & 3       & 2.5 \\
  2 & C     & C    & 3       & 2.75 \\
\end{tabular}

\drafting So here satisficing play finds a Pareto optimal action, but it doesn't find
the best possible action it could get against this opponent. From this example
we can also see how dependent satisficing play is on its starting parameters.
\todo{here we can interject an intermezo, of how karandikar tried to solve
this with trajection and random pertrubations}

\drafting And finally versus tit for tat, a game which can also be found in the
\citep{stimpson:2001} paper:

\begin{tabular}{lllll}
        t & TT & $A_t$ & $\pi_t$ & $\alpha_t$ \\
        0 & C     & C    & 3       & 4  \\
        1 & C     & D    & 4       & 3.5 \\
        2 & D     & D    & 2       & 3.75 \\
        3 & D     & C    & 1       & 2.87 \\
        4 & C     & D    & 4       & 3.435 \\
        5 & D     & D    & 2       & 2.715 \\
        6 & D     & C    & 1       & 1.85875 \\
\end{tabular}
\section{Properties of satisficing play}
\drafting

>>>>

\section{Satisficing play in action}
\todo{make an intermezzo of this?}
\drafting
To demonstrate a potential use of this algorithm we will use at several example
cases. The first one being the iterated prisoner's dilemma. Consider
the following normal form game:

@@

\begin{tabular}{lllll}
    t & Cooperate & $A_t$ & $\pi_t$ & $\alpha_t$ \\
    0 & C     & C    & 2       & 3 \\
    1 & C     & D    & 3       & 2.5 \\
    2 & C     & D    & 3       & 2.75 \\
\end{tabular}

@@

\begin{tabular}{lllll}
  t & Coop & $A_t$ & $\pi_t$ & $\alpha_t$ \\
  0 & C     & C    & 2       & 1 \\
  1 & C     & C    & 2       & 1.5 \\
  2 & C     & C    & 2       & 1.75 \\
\end{tabular}

\drafting So here satisficing play finds a Pareto optimal action, but it doesn't find
the best possible action it could get against this opponent. From this example
we can also see how dependent satisficing play is on its starting parameters.
\todo{here we can interject an intermezzo, of how karandikar tried to solve
this with trajection and random perturbations}

\drafting Now consider a game versus tit for tat (TT), Tit for Tat is a
strategy that always copies the last action of its opponent.
This game can also be found in the \citep{stimpson:2001} paper:

\begin{tabular}{lllll}
        t & TT & $A_t$ & $\pi_t$ & $\alpha_t$ \\
        0 & C     & C    & 2       & 3  \\
        1 & C     & D    & 3       & 2.5 \\
        2 & D     & D    & 1       & 2.75 \\
        3 & D     & C    & 0       & 1.87 \\
        4 & C     & D    & 3       & 2.435 \\
        5 & D     & D    & 1       & 1.715 \\
        6 & D     & C    & 0       & 0.85875 \\
\end{tabular}

In this table we can see satisficing play and tit for tat ending up in a cycle.
at $t=0$ satisficing gained to little reward for its ambition level $\alpha_t$,
and therefore switches action in the next round. In $t=1$ saticificing play
is satisfied, but int $t=2$ it no longer is so it switches but this even ends
up being worse at $t=3$. After that the cycle resets at $t=4$, the cycle becomes
most obvious when looking at the $\pi_t$ column.
\section{Properties of satisficing play}
\drafting
